---
title: "Computational Musicology Project"
output:
    flexdashboard::flex_dashboard:
      storyboard: true
      theme: flatly
author: Ananta Wibisono
      
date: "2024-02-14"
---

```{r asdfsadf, echo=FALSE}
library(spotifyr)
krnb <- get_playlist_audio_features("", "37i9dQZF1EIecOSIx69OSk")
kpop <- get_playlist_audio_features("", "37i9dQZF1EQpesGsmIyqcW")
krnb_general <- get_playlist_audio_features("", "2TJHOlrTUoLMHs9CTyxN9n")
krnb_general_50 <- head(krnb_general, 50)
kpop_general <- get_playlist_audio_features("", "37i9dQZF1DX9tPFwDMOaN1")

kpop_general_sorted <- kpop_general[order(kpop_general$energy), ]

# Remove the 5 lowest energy tracks
kpop_general_49 <- kpop_general_sorted[-(1:5), ]



warr <- get_track_audio_features(c("1ZEFYW6nPEvIcsIvymgsLk", "3DBKc4ioGnMQLlbGQcFDIO"))

library(ggplot2)
library(plotly)
library(dplyr)
library(tibble)

```
Overview
========================================
### Corpus Description

My corpus consists of 2 playlist of songs that i listen to of western pop songs and k-pop songs that contain 50 tracks each, and 2 playlists of western and k-pop songs in general. The reason I chose this is because i’m an avid listener of kpop and I have some favourite pop songs. My reason for choosing my corpus is because I want to figure out the differences between western pop songs and the ever more popular kpop genre and also what makes me like certain pop songs and if there exists a common factor within kpop and western pop songs that i like. I will be choosing the personal mix for kpop and western pop and furthermore curated playlists for kpop and western pop made by spotify themselves. This assures represenativeness. Furthermore there are no atypical songs in the corpus that is chosen

Difference in Tempo
========================================



Column {data-width=500}
-------------------------------------

### Plot: Difference in Tempo

```{r difference in tempo, echo=FALSE}
# Calculate mean values
krnb_mean <- mean(krnb$energy)
kpop_mean <- mean(kpop$energy)
gen_krnb_mean <- mean(krnb_general_50$energy)
gen_kpop_mean <- mean(kpop_general_49$energy)

# Plot with mean lines
histies <- ggplot() +
  geom_histogram(data = krnb, aes(x = energy, fill = "Personal Korean R&B Mix"), alpha = 0.5) +
  geom_histogram(data = kpop, aes(x = energy, fill = "Personal K-POP Mix"), alpha = 0.5) +
  geom_histogram(data = krnb_general_50, aes(x = energy, fill = "General Korean R&B"), alpha = 0.5) +
  geom_histogram(data = kpop_general_49, aes(x = energy, fill = "General K-POP"), alpha = 0.5) +
  geom_vline(xintercept = krnb_mean, color = "green", linetype = "twodash", size = 0.5) + 
  geom_vline(xintercept = kpop_mean, color = "red", linetype = "twodash", size = 0.5) +    
  geom_vline(xintercept = gen_krnb_mean, color = "blue", linetype = "twodash", size = 0.5) + 
  geom_vline(xintercept = gen_kpop_mean, color = "yellow", linetype = "twodash", size = 0.5) +  
  scale_fill_manual(name = "Genre", values = c("Personal Korean R&B Mix" = "green", "Personal K-POP Mix" = "red", "General Korean R&B" = "blue", "General K-POP" = "yellow" )) +
  theme(legend.position = "right") + labs(title = "Energy Difference between Krnb and Kpop") + theme_classic() 

histies <- ggplotly(histies)

histies
```
Column {data-width=500}
-------------------------------------

**Summary**

In this plot I pulled in data of 4 different playlists: 

1. My Personal KrnB playlist
2. My Personal Kpop playlist
3. A curated KRnB playlist
4. A curated KPOP playlist

Lets only view the personal playlists for now by clicking on the legend of the interactive plot. 

For these playlists I hypothesized that the KPOP playlist would have a higher mean energy level than the krnb playlist. This hypothesis turned out to be true when looking at the histogram plot. Besides the mean energy level indeed being higher for KPOP songs, you can also see a slight overlap with some krnb and kpop songs having the same energy levels. An interesting finding is that there are some krnb songs that fall in the upper spectrum of the energy level of even the KPOP song category: 

```{r show high energy level songs, echo=FALSE}
krnb_show <- krnb[order(krnb$energy, decreasing = TRUE), c("energy", "track.name")]

krnb_show %>%
  slice_head(n = 2) %>%
  knitr::kable()

```

Relation between loudness and energy
========================================

Column {data-width=500}
-------------------------------------

### Plot: Relation between loudness and energy

```{r energy plot, echo=FALSE}
corr_plot <- ggplot() +
  geom_point(data = krnb, aes(energy, loudness, color = "krnb"), alpha = 0.7) +
  geom_point(data = kpop, aes(energy, loudness, color = "kpop"), alpha = 0.7) +
  # Calculate and add a linear regression line through all points
  geom_smooth(data = rbind(krnb, kpop), aes(energy, loudness), method = "lm", se = FALSE, color = "red", alpha = 0.7) +
  scale_color_manual(values = c("krnb" = "blue", "kpop" = "pink"),
                     labels = c("kpop", "krnb"),
                     name = "Genres") + labs(title = "Relation between loudness and energy")

corr_plot <- ggplotly(corr_plot)

corr_plot
```

Column {data-width=500}
-------------------------------------

**Summary**

In this plot i hyposthesised that energy and loudness had a correlation and it was shown to be indeed the case, this is even more shown by the regression line that is ran through the data points. You can also see a slight boundry line being present between kpop an krnb songs. Besides that there is again 1 outlier but in this case i want to highlight the 1 kpop song that falls in the krnb category in terms of loudness


