---
title: "Computational Musicology Project"
output:
    flexdashboard::flex_dashboard:
    storyboard: true
    theme: plotly
      
date: "2024-02-14"
---

```{r asdfsadf, echo=FALSE}
library(spotifyr)
krnb <- get_playlist_audio_features("", "37i9dQZF1EIecOSIx69OSk")
kpop <- get_playlist_audio_features("", "37i9dQZF1EQpesGsmIyqcW")
krnb_general <- get_playlist_audio_features("", "2TJHOlrTUoLMHs9CTyxN9n")
krnb_general_50 <- head(krnb_general, 50)
kpop_general <- get_playlist_audio_features("", "37i9dQZF1DX9tPFwDMOaN1")

kpop_general_sorted <- kpop_general[order(kpop_general$energy), ]

# Remove the 5 lowest energy tracks
kpop_general_filtered <- kpop_general_sorted[-(1:5), ]

kpop_general_filtered

warr <- get_track_audio_features(c("1ZEFYW6nPEvIcsIvymgsLk", "3DBKc4ioGnMQLlbGQcFDIO"))



```

Difference in Tempo
========================================


```{r stuff, echo=FALSE}
library(ggplot2)
library(plotly)
```


### Plot: Difference in Tempo

**Summary**

In this plot I pulled in data of 4 different playlists: 

1. My Personal KrnB playlist
2. My Personal Kpop playlist
3. A curated KRnB playlist
4. A curated KPOP playlist

Lets only view the personal playlists for now

For these playlists I hypothesized that the KPOP playlist would have a higher mean energy lever than the krnb playlist. This hypothesis turned out to be true when looking at the histogram plot. Besides the mean energy level indeed being higher for KPOP songs, you can also see a slight overlap with some krnb and kpop songs having the same energy levels. An interesting finding is that there are some krnb songs that fall in the upper spectrum of the energy level of even the KPOP song category. 

```{r show high energy level songs, echo=FALSE}
krnb_show <- krnb[order(krnb$energy, decreasing = TRUE), c("energy", "track.name")]

krnb_show

```


```{r difference in tempo, echo=FALSE}
# Calculate mean values
krnb_mean <- mean(krnb$energy)
kpop_mean <- mean(kpop$energy)
gen_krnb_mean <- mean(krnb_general$energy)
gen_kpop_mean <- mean(kpop_general$energy)

# Plot with mean lines
histies <- ggplot() +
  geom_histogram(data = krnb, aes(x = energy, fill = "Personal Korean R&B Mix"), alpha = 0.5) +
  geom_histogram(data = kpop, aes(x = energy, fill = "Personal K-POP Mix"), alpha = 0.5) +
  geom_histogram(data = krnb_general_50, aes(x = energy, fill = "General Korean R&B"), alpha = 0.5) +
  geom_histogram(data = kpop_general, aes(x = energy, fill = "General K-POP"), alpha = 0.5) +
  geom_vline(xintercept = krnb_mean, color = "green", linetype = "twodash", size = 0.5) + 
  geom_vline(xintercept = kpop_mean, color = "red", linetype = "twodash", size = 0.5) +    
  geom_vline(xintercept = gen_krnb_mean, color = "blue", linetype = "twodash", size = 0.5) + 
  geom_vline(xintercept = gen_kpop_mean, color = "yellow", linetype = "twodash", size = 0.5) +  
  scale_fill_manual(name = "Genre", values = c("Personal Korean R&B Mix" = "green", "Personal K-POP Mix" = "red", "General Korean R&B" = "blue", "General K-POP" = "yellow" )) +
  theme(legend.position = "right") + labs(title = "Energy Difference between Krnb and Kpop") + theme_classic()

histies <- ggplotly(histies)

histies
```

Relation between loudness and energy
========================================

### Plot: Relation between loudness and energy

```{r energy plot, echo=FALSE}
corr_plot <- ggplot() +
  geom_point(data = krnb, aes(energy, loudness, color = "krnb"), alpha = 0.7) +
  geom_point(data = kpop, aes(energy, loudness, color = "kpop"), alpha = 0.7) +
  # Calculate and add a linear regression line through all points
  geom_smooth(data = rbind(krnb, kpop), aes(energy, loudness), method = "lm", se = FALSE, color = "red", alpha = 0.7) +
  scale_color_manual(values = c("krnb" = "blue", "kpop" = "pink"),
                     labels = c("kpop", "krnb"),
                     name = "Genres") + labs(title = "Relation between loudness and energy")

corr_plot <- ggplotly(corr_plot)

corr_plot
```